\begin{thebibliography}{8}
\bibitem{ref_article1}
Rathore, Neeraj: Ethical Hacking \& Security against Cyber Crime. i.-manager's Journal on Information Technology \textbf{5}(1), 13--17 (2015-2016)

\bibitem{ref_url1}
Forbes, \url{https://www.forbes.com/sites/daveywinder/2020/01/29/google-confirms-it-will-pay-android-pixel-hackers-15-million/?sh=2dbb025833ab}. Last accessed 15 Dec 2021

\bibitem{ref_url2}
techjury, \url{https://techjury.net/blog/how-many-cyber-attacks-per-day/}. Last accessed 15 Dec 2021

\bibitem{ref_url3}
University of Maryland, \url{https://eng.umd.edu/news/story/study-hackers-attack-every-39-seconds}. Last accessed 15 Dec 2021

\bibitem{ref_url4}
Wired, \url{www.wired.com/story/worst-hacks-of-the-decade}. Last accessed 15 Dec 2021

\bibitem{haystack_ids}
I. Kandrouch, N. Hmina, H. Chaoui
:A Novel Security Architecture Based on 
Haystack System for HDFS Storage System: 
Extended Work, S. 714, (2020)

\bibitem{IDS_Book_1}
Roberto Di Pietro, Luigi V. Mancini: Intrusion Detection Systems, S. 173, (2008)

\bibitem{IDS_Book_2}
William Stalling, Lorie Brown: Computer Security Principles and Practices, 4th Edition, S. 278 - 306, (2018) 

\bibitem{url_sensors}
Wired, \url{https://www.informit.com/articles/article.aspx?p=782118}. Letzter Zugriff: 23. Dec 2021

\bibitem{ref_book_attack_1}
Martin Kappes: Netzwerk- und Datensicherheit, S. 141-142, 2nd edn Springer Vieweg (2013)
\bibitem{ref_book_attack_2}
Martin Kappes: Netzwerk- und Datensicherheit, S. 249, 2nd edn Springer Vieweg (2013)
\bibitem{ref_book_attack_3}
Martin Kappes: Netzwerk- und Datensicherheit, S. 250-251, 2nd edn Springer Vieweg (2013)

\bibitem{ref_book_attack_4}
Steffen Wendzel: IT-Sicherheit für TCP/IP- und IoT-Netzwerke, 1st edn Springer Vieweg S. 212-213 (2018)
\bibitem{ref_book_attack_5}
Steffen Wendzel: IT-Sicherheit für TCP/IP- und IoT-Netzwerke, 1st edn Springer Vieweg S. 213-214 (2018)
\bibitem{ref_book_attack_6}
Steffen Wendzel: IT-Sicherheit für TCP/IP- und IoT-Netzwerke, 1st edn Springer Vieweg S. 233 (2018)

\bibitem{ref_book_attack_7}
Claudia Eckert: IT-Sciherheit, 10th edn De Gruyter Oldenburg S. 75-76 (2018)

\bibitem{ref_url5}
Virtual Box Homepage, \url{https://www.virtualbox.org/wiki/Virtualization} \url{https://www.virtualbox.org/}. Letzter Zugriff: 45. Dec 2021

\bibitem{ref_url6}
Kali Homepage, \url{https://www.kali.org/features/}. Letzter Zugriff: 14. Dec 2021

\bibitem{ref_url7}
Nmap Homepage, \url{https://nmap.org/man/de/index.html}. Letzter Zugriff: 14. Dec 2021

\bibitem{ref_url8}
Wireshark Homepage, \url{https://www.wireshark.org}. Letzter Zugriff: 14. Dec 2021

\bibitem{ref_url9}
Cloudflare Learning, \url{ https://www.cloudflare.com/de-de/learning/ddos/ddos-attack-tools/how-to-ddos/}. Letzter Zugriff: 15 Dec 2021

\bibitem{ref_url10}
Geekflare Homepage, \url{https://geekflare.com/de/mitm-attack-tools/}. Letzter Zugriff: 15 Dec 2021 Letzter Zugriff: 15 Dec 2021

\bibitem{ref_ieee_attack_8}
Mauro Conti, Nicola Dragoni, Viktor Lesyk: A Survey of Man In The Middle Attacks \url{https://ieeexplore.ieee.org/abstract/document/7442758}. Letzter Zugriff: 25 Dec 2021

\bibitem{ref_url11}
Ionos Homepage, \url{https://www.ionos.de/digitalguide/server/sicherheit/man-in-the-middle-attack-angriffsmuster-im-ueberblick/} Letzter Zugriff: 25 Dec 2021

\bibitem{ref_url12}
Ionos Homepage, \url{https://www.ionos.de/digitalguide/server/sicherheit/dns-spoofing/} Letzter Zugriff: 25 Dec 2021

\bibitem{ref_ieee_attack_9}
Mohammed I. Al-Saleh, Ziad A. Al-Sharif,  Luay Alawneh: Network Reconnaissance Investigation: A Memory Forensics Approach \url{https://ieeexplore.ieee.org/document/8809084} Letzter Zugriff: 28. Dec 2021

\bibitem{ref_url13}
Types of Footprinting in Ethical Hacking, \url{https://www.geeksforgeeks.org/types-of-footprinting-in-ethical-hacking/?ref=rp} Letzer Zugriff: 28. Dec 2021

\bibitem{ref_url14}
Ethical Hacking | Footprinting, \url{https://www.geeksforgeeks.org/ethical-hacking-footprinting/} Letzter Zugriff: 28. Dec. 2021

\bibitem{ref_url15}
Avast Homepage: Port Scans, \url{https://www.avast.com/de-de/business/resources/what-is-port-scanning} Letzter Zugriff: 28. Dec 2021

\bibitem{ref_url16}
Nmap Man Page, \url{https://nmap.org/man/de/man-misc-options.html} Letzter Zugriff: 28. Dec 2021

\bibitem{ref_url17}
Grey Campus, \url{https://www.greycampus.com/opencampus/ethical-hacking/enumeration-and-its-types} Letzter Zugriff: 28. Dec 2021

\bibitem{snort_book_1}
Caswell B., Baker A., Beale J.: Snort Intrusion Detection and Prevention Toolkit,
(2007)

\bibitem{snort_url}
Snort Homepage, \url{https://www.snort.org/} Letzter Zugriff: 27 Dec 2021

\bibitem{hids_url_1}
Heimdal Security Homepage, \url{https://heimdalsecurity.com/blog/host-intrusion-detection-system-hids/} Letzter Zugriff: 27 Dec 2021

\bibitem{hids_url_2}
Redscan Homepage, \url{https://www.redscan.com/services/managed-intrusion-detection-system/hids/} Letzter Zugriff: 27 Dec 2021



% http://infosecwriters.com/text_resources/pdf/Footprinting.pdf



%\bibitem{ref_lncs1}
%Author, F., Author, S.: Title of a proceedings paper. In: Editor,
%F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
%Springer, Heidelberg (2016). \doi{10.10007/1234567890}

%\bibitem{ref_book1}
%Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
%Location (1999)

%\bibitem{ref_proc1}
%Author, A.-B.: Contribution title. In: 9th International Proceedings
%on Proceedings, pp. 1--2. Publisher, Location (2010)

%\bibitem{ref_url2}
%LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
%Oct 2017
\end{thebibliography}